Transform and Tell:\\The News Image Caption Writer That Remembers Rare Names

### 2019-11-14 paper/section_5_experiments.tex
Add changes from Alex on experiments

In all experiments, we use Adam~\cite{Kingma2015Adam} with the weight decay fix
\cite{Loshchilov2018DecoupledWD} to optimize the models. We use the following
parameters: $\beta_1 = 0.9, \beta_2 = 0.98, \epsilon = 10^{-6}$, and a weight
decay of $10^{-5}$. We clip the gradient norm at 0.1. All models see the same
number of training examples, which is 6.6 million. This is equivalent to 16
epochs through GoodNews and 9 epochs through NYTimes800k. We warm up the
learning rate in the first 5\% of the training steps to $10^{-4}$, and decays
it linearly afterwards. Training is done with mixed precision to reduce the
memory footprint. The full model takes 5 days to train on one Titan V GPU.

@@

@@

Table~\ref{tab:results} shows the BLEU~\cite{Papineni2002Bleu}, ROUGE
\cite{Lin2004ROUGE}, METEOR~\cite{Denkowski2014Meteor}, and CIDEr
\cite{Vedantam2015CIDEr} metrics on GoodNews and NYTimes800k. We show two best
results from the previous state-of-the-art~\cite{Biten2019GoodNews}. Note that
the numbers reported here are slightly different from the original paper since
we had to remove a few samples from the test set where the image is no longer
available.~\cite{Biten2019GoodNews} also did some post-processing on the
ground-truth captions such as removing contractions and non-ASCII characters,
both of which we did not do. Despite these differences, the final metrics
are the same if rounded to the nearest whole number.

>>>>

For parameter optimisation we use the adaptive gradient algorithm
Adam~\cite{Kingma2015Adam} with the following
parameter settings: $\beta_1 = 0.9, \beta_2 = 0.98, \epsilon = 10^{-6}$. We
warm up the
learning rate in the first 5\% of the training steps to $10^{-4}$, and decay
it linearly afterwards.

We apply $L_2$ regularisation to all network weights with a value of $10^{-5}$
and use the weight decay fix~\cite{Loshchilov2018DecoupledWD} to decouple the
learning rate from the regularisation parameter. We clip the gradient norm at
0.1. We \verify{ use a batch size of ****** and train all models for 6.6 million
steps}. This is equivalent to 16
epochs on GoodNews and 9 epochs on NYTimes800k. Training is done with mixed
precision to reduce the
memory footprint and allow our full model to be trained on a single GPU. This
full model
takes 5 days to train on one Titan V GPU and
has 207 million trainable parameters -- see the supplement for the number of
trainable parameters in each model variant.

@@

\subsection{Evaluation Metrics}

We use BLEU~\cite{Papineni2002Bleu}, ROUGE
\cite{Lin2004ROUGE}, METEOR~\cite{Denkowski2014Meteor}, and CIDEr
\cite{Vedantam2015CIDEr} scores as they are standard for evaluating image
captions. These are obtained using the COCO
caption evaluation toolkit
\footnote{\href{https://github.com/tylin/coco-caption}
{https://github.com/tylin/coco-caption}}. In addition, we evaluate the
precision and recall on: named entities, personal names, and rare proper names.
\verify{Named entities are identified in both the ground truth captions and
the generated
captions using the SpaCy~\cite{} natural language processing toolkit. We then
count exact string matches between the ground truth entities and generated
entities.
For personal names we restrict the set of named entities to those marked as
PERSON by the SpaCy parser. Rare proper nouns are nouns (as identified by the
SpaCy Parts-of-Speech tagger) that occur less than ******** times in the
training
dataset.}

@@

Table~\ref{tab:results} shows the BLEU, ROUGE
,METEOR, and CIDEr metrics on GoodNews and NYTimes800k. We show two best
results from the previous state-of-the-art~\cite{Biten2019GoodNews}. Note that
the numbers reported here are slightly different from the original paper since
we had to remove a few samples from the test set where the image is no longer
available.~\cite{Biten2019GoodNews} also did some post-processing on the
ground-truth captions such as removing contractions and non-ASCII characters,
both of which we did not do. Despite these differences, the final metrics
are the same if rounded to the nearest whole number.
